iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-30 manuscript/main.tex

\section{Competing interests}
No competing interests were declared.

\section{Grant information}
ATLL was supported by core funding from Cancer Research UK (award no. 17197 to Dr.\ John Marioni).
The work of FM is supported by the German Federal Ministry of Education and Research (BMBF 01EO1003).

\section{Acknowledgements}
We thank the organizers and participants of the European Bioconductor Meeting 2017, where the idea for this package was first conceived.
We also thank members of the Bioconductor community for their helpful suggestions.

>>>>

\section*{Competing interests}
No competing interests were declared.

\section*{Grant information}
ATLL was supported by core funding from Cancer Research UK (award no. 17197 to Dr.\ John Marioni).
The work of FM is supported by the German Federal Ministry of Education and Research (BMBF 01EO1003).

\section*{Acknowledgements}
We thank the organizers and participants of the European Bioconductor Meeting 2017, where the idea for this package was first conceived.
We also thank members of the Bioconductor community for their helpful suggestions.
